LSOA domestic Electricty and Gas maps

### 2021-08-21 LSOA domestic Elec and Gas.Rmd
Changing some typos in the cities in more detail section

#####Cities in more detail
```{r Southampton LSOA difference in dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LSOA11CD == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
#BROKEN
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de-diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

@@

```{r Mapping the change in LSOA dom mean gas comsumption}
merged_dgas$LSOA11CD <- merged_dgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
ggplot2::ggplot(merged_dgas) +
  geom_sf(aes(fill=dg_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)") ##BROKEN
```

>>>>

#####Cities in more detail
```{r Southampton LSOA difference in dom Elec}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LSOA11CD == "Southampton")
# plotting the electricity consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Southampton")
#BROKEN
```
```{r Portsmouth LSOA difference in dom Elec}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LSOA11CD == "Portsmouth")
# plotting the electricity consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de-diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA difference in dom Elec}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_de, LAD11NM == "Winchester")
# plotting the electricity consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `de_diff`)) +
  scale_fill_continuous(name = "Change in Mean comsumpton (kWh per meter)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

@@

```{r Mapping the change in LSOA dom mean gas comsumption}
merged_dgas$LSOA11CD <- merged_dgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_dgas20102019 <- merge(lsoa_sf_data, merged_dgas) #merging these
ggplot2::ggplot(merged_dgas) +
  geom_sf(aes(fill=dg_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)") ##BROKEN
##Need to change the varibale names to reflect what is actually there
```
